\vspace{-1in} Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A Guide for International Students

### 2023-10-06 demystify.tex
update

\subsection{Should you contact a US professor? What to do to get a desired reply?}

@@

If you want to contact a prof. to ask about \emph{research opportunities}, or \emph{GTA/GRA} support, then \emph{yes}, I believe you should---it is \emph{worth it}. However, you need to do it the \emph{right way}.

First, read the prof's website, see if they say something about contacting them. Many profs. indicate how prospective students should contact them (e.g., using specific email subjects). 
In general, the best way to catch the prof.'s attention is to \emph{customize your email} to that faculty.  For example, read their papers, know what they work on, and see if you are interested in their research. Then send them an email talking how/why their work would match yours.
In contrast, if you write a generic email that can be sent to multiple professors (e.g., if you just change some names and keywords in the email), you will not get a response.

>>>>

\subsection{Should you contact a professor? What to do to get a desired reply?}

@@

If you want to contact a prof. to ask about \emph{research opportunities}, or \emph{funding} support, then \emph{yes}, I believe you should---it is \emph{worth it}. However, you need to do it the \emph{right way}.

First, read the prof's website, see if they say something about contacting them. Many profs. explicitly indicate how prospective students should contact them (e.g., using specific email subjects). 
In general, the best way to catch the prof.'s attention is to \emph{customize your email} for them.  For example, read their papers, know what they work on, and see if you are interested in their research. Then send them an email talking how/why their work would match yours.
In contrast, if you write a generic email that can be sent to multiple professors (e.g., if you just change some names and keywords in the email), you will not get a response.
